---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
library(dplyr)
library(knitr)

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# inconData - Datasets for instantaneous consonance perception

[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.2545785.svg)](https://doi.org/10.5281/zenodo.2545785)

This package compiles several empirical datasets for experiments on instantaneous consonance perception.

## Installation

You can install the current version of `inconData` from Github
by entering the following commands into R:

``` r
if (!require(devtools)) install.packages("devtools")
devtools::install_github("inconData")
```

## Datasets

Currently the following datasets are included:

```{r, echo = FALSE}
library(inconData)
incon_datasets() %>% 
  rename(Label = label,
         Description = description) %>% 
  kable()
```


See the inbuilt package documentation (e.g. `jl12a`)
for details of the specific datasets.
